Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-17 Paper.tex
Fixed citation.

The scheme we use in order to generate consensus is a simplified version of the GHOST algorithm \cite{ghost}. This process is described in detail in section \ref{ch:ghost}.

@@

Vitalik Buterin first proposed in the original Ethereum whitepaper (first distributed in December 2013) moving from a single state-transaction function with trivial state to something much more general and expansive. Useful corrections and suggestions were provided by a number of others from the Ethereum community including Aeron Buchanan

@@

The method of signing transactions is similar to the `Electrum style signatures'; it utilises the SECP-256k1 curve.

>>>>

The scheme we use in order to generate consensus is a simplified version of the GHOST protocol \cite{cryptoeprint:2013:881}. This process is described in detail in section \ref{ch:ghost}.

@@

Vitalik Buterin first proposed in the original Ethereum whitepaper (first distributed in December 2013) moving from a suffocating state-transaction function with trivial state to something much more general and expansive. Useful corrections and suggestions were provided by a number of others from the Ethereum community including Aeron Buchanan, Nick Savers and Marko Simovic.

@@

The method of signing transactions is similar to the `Electrum style signatures'; it utilises the SECP-256k1 curve. This has yet to be formally specified.
